 
\documentclass[margin=<value>,11pt]{res} % default is 10 pt
% margin option puts section titles to left of text
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage[brazilian]{babel}
\usepackage[a4paper]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}

\begin{document}
\name{PEDRO PAULO VEZZÁ CAMPOS\\[12pt]} % the \\[12pt] adds a blank line after name

\address{R. Indiana, 998 -- São Paulo, SP 04562-001 -- Brazil\\
        (+55 11) 97132-1145, (+55 11) 2389-7150 \\ \texttt{pedro@vezza.com.br}}
%\address{ {\bf Permanent Address} \\ 29 Amorous Avenue \\ Madison, NJ 07940 \\
%         (201) 777-3821 }

\begin{resume}
 
\section{GOAL}
	Develop solutions in Cloud Computing and Computer Networks.
 
\section{SUMMARY}
I'm a senior year CS undergraduate student at the Institute of Mathematics and Statistics of the University of São Paulo (IME-USP). My education is very versatile by having being exposed to different experiences during undergraduation. I've started my studies at the Federal University of Santa Catarina (UFSC) as the first placed student at the admition exam for CS and 89\textsuperscript{th} in the general classification. In my sophomore year I was invited to a student scholarship in Microeletronics. After that, I was the only admitted in the transfer exam to IME-USP, famous for its mathematical and algorithmic focus. There, I've practiced these skills as a participant in the ACM-ICPC International Collegiate Programming Contest. Still, I've started my second student scholarship, in the area of CS education, which allowed me to have a broad view of the career. I'm willing to work in development of solutions in Cloud Computing and Computer Networks. I'm a certified solution advisor in Cloud Computing by IBM. Also, I'm free to relocate, having lived in seven different cities in four different states in Brazil.

\section{EXPERIENCE}
	{\bf University of São Paulo} \\
		\begin{ncolumn}{2} % produces two equally spaced columns
		\underline{Scientific Scholarship}     &      03/2012 - Today
		\end{ncolumn}
		I work at the Apoio BCC project, which aims to lower the IME-USP Computer Science course evasion thru course contextualization efforts, different CS curricula analysis and researching course egresses. I'm co-responsible for the application and analysis of questionnaires applied to ex-undergraduate students with the intent to find academic trends in the job market, suggestions and critics to the course. Moreover, I study and present national, international and reference curricula to aid the IME-USP CS curriculum reformulation process.


	{\bf Federal University of Rio Grande do Sul} \\
		\begin{ncolumn}{2} % produces two equally spaced columns
		\underline{Technological and Industrial Scholarship}     &      03/2010 - 12/2010
		\end{ncolumn}
		Scholarship student at the SisRas -- Reliable, Available and Serviceable Systems project held by the Federal University of Rio Grande do Sul. The main area of research was the study and design of fault tolerant fast adders. Others studies included the improvement of tools to simulate scratchpad memories (SPM). Research held at the System Design Automation Lab at the Federal University of Santa Catarina.
 
\section{STUDY} 
	{\bf University of São Paulo}\\
	BSc in Computer Science \\
	2011 - 2013 \\
	GPA: 8,7/10 \\
	Expected graduation in late 2013

	{\bf Federal University of Santa Catarina}\\
	BSc in Computer Science \\
	2009 - 2010 \\
	GPA: 9,48/10 \\
	Transferred to USP \\

\section{RECOGNITIONS}
	{\bf Academic Performance Certificate 2009/1, 2009/2, 2010/1, 2010/2}\\
	Federal University of Santa Catarina\\
	february 2013

\section{LANGUAGES}
	\begin{ncolumn}{3}
	{\bf Portuguese} & {\bf English}        & {\bf French} \\
	Native    & Fluent & Basic  \\
	\end{ncolumn}

\section{PAPERS}
\begin{enumerate}
	\item \emph{Campos, P. P. V.; Souza, J.; Olguin, G.} . \textbf{A Survey on the Mathematical Emphasis in Brazilian Computer Science Curricula}. To be presented at the 2013 Frontiers in Education Conference, 2013, Oklahoma City, USA.
	\item \emph{Monteiro, J. L. ; Campos, P. P. V. ; Guntzel, J. L. A. ; Agostini, L.} . \textbf{Cell-Based VLSI Implementations of the Add One Carry Select Adder}. In: 26th South Symposium on Microelectronics, 2011, Novo Hamburgo, Brazil.
\end{enumerate}


\section{CERTIFICATES}
{\bf Certified Solution Advisor - Cloud Computing Architecture V1}\\
IBM\\
september 2011

\end{resume} 
\end{document}





